The shape of dark matter halos in the AURIGA simulations

### 2019-03-05 Paper/paper.tex
edit

{\bf En este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
Figure \ref{fig:alignment} shows the cumulative distribution of
$\cos\theta$, where $\theta$ is the angle betwen the DM halo minor
axis and the stellar disk angular momentum.  
Each line shows the results at different radii.
We find that the majority of the disks are aligned with the minor axis
of their DM halo within $\approx 30^{\circ}$. 
Furthermore, if there is a good alignment measured at the virial
radius, this alignment is well conserved at smaller radii.
However, there are some disks that show string missalignments.

{\bf En este caso hace falta la figura de la evoluci\'on de cos theta
  como funci\'on del redshift}
To better understand the missalignments we plot the evolution of
$\cos\theta$ with the 
Figure \ref{fig:alignment_history}
\textit{This is an important result of our study. We study the radial
  evolution of the principal axes, compared also to the angular
  momentum vector from the disk. We found that while the angular
  momentum tend to be aligned with the minor axis of the ellipsoid,
  this may not be the case all times. When there is an alignment it is
  usually within 20 degrees (get a histogram of this. and an evolution
  of this histogram with time). When there is not an alignment, then
  there is no simple way to determine towards which axis it is
  oriented. Furthermore, the principal axes alignment usually change
  with radius (rotation, swap, verify). This ask for relaxation on the
  strong constrains on the MW DM halo models.}

>>>>

{\bf En este caso hace falta la figura con la distribuci\'on integrada de cos theta}.
Figure \ref{fig:alignment} shows the cumulative distribution of
$\cos\theta$, where $\theta$ is the angle betwen the DM halo minor
axis and the stellar disk angular momentum.  
Each line shows the results at different radii.
We find that the majority of the disks are aligned with the minor axis
of their DM halo within $\approx 30^{\circ}$. 
Furthermore, if there is a good alignment measured at the virial
radius, this alignment is well conserved at smaller radii.

{\bf En este caso hace falta la figura de la evoluci\'on de cos theta
  como funci\'on del redshift}
However, there are some disks that show strong missalignments. 
To better understand the missalignments we plot the evolution of
$\cos\theta$ with time to find that the missalignment has been present
for the last XXX Gyr.
This trend is summarized in Figure \ref{fig:alignment_history}.
